---
title: "WDI_poverty_analyzer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{WDI_poverty_analyzer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(Lujain)
library(dplyr)
```

## Use *World Data Institute* (WDI) Data to Explore Poverty

### Primary Aim:

Poverty and health equity is a major health topic. It is important for policy makers to make decisions based on data. My app will provide an interface to health and poverty data and analysis. Using this data might help them to find out what policy will work.


### Concept

The data is be taken from the World Data Bank (WDB). Using the R app `WDI` to download the data as the user requests it. 

WDB has lots of data, but the app presents the user with a good selection of that data. This saves the user from having explore the thousands of series on the website. 

The series can be categorized as follows (The user will choose from options in
these categories):

**Outcome measure:**

Outcome measurements related to poverty or economic health such as GINI index.

**Intervention:** 

Measurements of government intervention or things can be modified by government policies such as Income share held by fourth 20%. For example, the democrats claim that they can improve this number. 

**Confounders:**

Variables that cannot be modified by government policies such as age distribution, or ethnic variety. These will be used to adjust measures of the association between interventions and outcomes.

### The Data

The main data set is called `h`.  This contains selected series from the WDI website. 
One of the difficulties is finding series that have data.

```{r}
h %>% 
  filter(!is.na(SH.UHC.SRVS.CV.XD),!is.na(SL.UEM.NEET.FE.ZS)) %>% 
  head %>% knitr::kable()
```

### The shiny gadget: 

It takes dataset called h and produces a shiny interface.
The gadget asks the user for four inputs. They are the countries, series for the time plot and series for the scatter plot. 

### How to use the gadget: 

```{r}
h %>% poverty()
```


